### 2021-03-30 README.Rmd
new data/function, pilot mode

- `add_archigos()`: adds some summary variables from Archigos about political leaders for state-year or dyad-year data.
- `add_atop_alliance()`: adds ATOP alliance information to dyad-year data.
- `add_capital_distance()`: adds capital-to-capital distance (in kilometers, "as the crow flies") to dyad-year or state-year data.
- `add_contiguity()`: adds Correlates of War direct contiguity data to dyad-year or state-year data.
- `add_cow_alliance()`: adds Correlates of War major alliance information to dyad-year data.
- `add_cow_majors()`: adds Correlates of War major power information to dyad-year or state-year data.
- `add_cow_trade()`: adds Correlates of War trade data to dyad-year or state-year data.
- `add_democracy()`: adds estimates of democracy/levels of democracy to dyad-year or state-year data.
- `add_gwcode_to_cow():` adds Gleditsch-Ward state codes to dyad-year or state-year data with Correlates of War state codes.
- `add_igos()`: adds Correlates of War International Governmental Organizations (IGOs) data to dyad-year or state-year data.
- `add_mids():` adds dyad-year information about ongoing MIDs and MID onsets from the Gibler-Miller-Little data.
- `add_minimum_distance()`: adds minimum distance (in kilometers) to dyad-year or state-year data.
- `add_nmc()`: adds estimates of national material capabilities (from Correlates of War) to dyad-year or state-year data.
- `add_sdp_gdp()`: adds estimates of (gross and surplus) domestic product and population size to dyad-year or state-year data
- `create_dyadyears()`: converts Correlates of War or Gleditsch-Ward state system membership data into dyad-year format
- `create_statedays()`: converts Correlates of War or Gleditsch-Ward state membership data into state-day format..
- `create_stateyears()`: converts Correlates of War or Gleditsch-Ward state membership data into state-year format.
- `filter_prd()`: filters dyad-year data frame to just "politically relevant" dyads.

@@

- `archigos`: an abbreviated version of the Archigos data, used internally
- `atop_alliance:` directed dyad-year alliance data from ATOP
- `capitals`: a list of capitals and capital transitions for Correlates of War state system members
- `ccode_democracy`: Correlates of War state-year data with three different estimates of democracy (Varieties of Democracy, Polity, Xavier Marquez/Pemstein et al.'s "(Quick) Unified Democracy Scores").
- `cow_alliance`: directed dyad-year alliance formation data from the Correlates of War
- `cow_contdir`: Correlates of War Direct Contiguity Data (v. 3.2)
- `cow_ddy`: a full directed dyad-year data frame of Correlates of War state system members
- `cow_gw_years`: a yearly data frame including information about Correlates of War and Gleditsch-Ward states.
- `cow_igo_ndy`: non-directed dyad-year data for Correlates of War intergovernmental organizations data.
- `cow_igo_sy`: state-year data for Correlates of War intergovernmental organizations data.
- `cow_majors`: Correlates of War major powers data (version: 2016)
- `cow_mindist`: the minimum distance between Correlates of War states, in kilometers, in non-directed dyad-year format (1946-2015)
- `cow_nmc`: Correlates of War National Material Capabilities data (version 5.0)
- `cow_sdp_gdp`: (Surplus and Gross) Domestic Product for Correlates of War States
- `cow_states`: Correlates of War state system membership data (version: 2016)
- `cow_trade_sy`: Correlates of War state-year trade data (version 4.0)
- `gml_dirdisp`: directed dispute-year data from version 2.1.1 of the Gibler-Miller-Little inter-state dispute data.
- `gw_ddy`: a full directed dyad-year data frame of Gleditsch-Ward state system members
- `gw_mindist`: the minimum distance between  Gleditsch-Ward states, in kilometers, in non-directed dyad-year format (1946-2015)
- `gw_sdp_gdp`: (Surplus and Gross) Domestic Product for Correlates of War States
- `gw_states`: Gleditsch-Ward independent state system data (version: 2017)
- `maoz_powers`: Zeev Maoz' global/regional power data.

@@

tic()
create_stateyears() %>%
  add_gwcode_to_cow() %>%
  add_capital_distance() %>%
  add_contiguity() %>%
  add_cow_majors() %>%
  add_cow_trade() %>%
  add_democracy() %>%
  add_igos() %>%
  add_minimum_distance(system = "cow") %>%
  add_archigos() %>%
  add_nmc() %>%
  add_sdp_gdp(system = "cow") 
toc()

>>>>

- `add_archigos()`: adds some summary variables from Archigos about political leaders for state-year or dyad-year data.
- `add_atop_alliance()`: adds ATOP alliance information to dyad-year data.
- `add_capital_distance()`: adds capital-to-capital distance (in kilometers, "as the crow flies") to dyad-year or state-year data.
- `add_contiguity()`: adds Correlates of War direct contiguity data to dyad-year or state-year data.
- `add_cow_alliance()`: adds Correlates of War major alliance information to dyad-year data.
- `add_cow_majors()`: adds Correlates of War major power information to dyad-year or state-year data.
- `add_cow_trade()`: adds Correlates of War trade data to dyad-year or state-year data.
- `add_democracy()`: adds estimates of democracy/levels of democracy to dyad-year or state-year data.
- `add_gwcode_to_cow():` adds Gleditsch-Ward state codes to dyad-year or state-year data with Correlates of War state codes.
- `add_igos()`: adds Correlates of War International Governmental Organizations (IGOs) data to dyad-year or state-year data.
- `add_mids():` adds dyad-year information about ongoing MIDs and MID onsets from the Gibler-Miller-Little data.
- `add_minimum_distance()`: adds minimum distance (in kilometers) to dyad-year or state-year data.
- `add_nmc()`: adds estimates of national material capabilities (from Correlates of War) to dyad-year or state-year data.
- `add_sdp_gdp()`: adds estimates of (gross and surplus) domestic product and population size to dyad-year or state-year data
- `add_ucdp_onsets()`: adds UCDP onsets to state-year data
- `create_dyadyears()`: converts Correlates of War or Gleditsch-Ward state system membership data into dyad-year format
- `create_statedays()`: converts Correlates of War or Gleditsch-Ward state membership data into state-day format..
- `create_stateyears()`: converts Correlates of War or Gleditsch-Ward state membership data into state-year format.
- `filter_prd()`: filters dyad-year data frame to just "politically relevant" dyads.

@@

- `archigos`: an abbreviated version of the Archigos data, used internally
- `atop_alliance:` directed dyad-year alliance data from ATOP
- `capitals`: a list of capitals and capital transitions for Correlates of War state system members
- `ccode_democracy`: Correlates of War state-year data with three different estimates of democracy (Varieties of Democracy, Polity, Xavier Marquez/Pemstein et al.'s "(Quick) Unified Democracy Scores").
- `cow_alliance`: directed dyad-year alliance formation data from the Correlates of War
- `cow_contdir`: Correlates of War Direct Contiguity Data (v. 3.2)
- `cow_ddy`: a full directed dyad-year data frame of Correlates of War state system members
- `cow_gw_years`: a yearly data frame including information about Correlates of War and Gleditsch-Ward states.
- `cow_igo_ndy`: non-directed dyad-year data for Correlates of War intergovernmental organizations data.
- `cow_igo_sy`: state-year data for Correlates of War intergovernmental organizations data.
- `cow_majors`: Correlates of War major powers data (version: 2016)
- `cow_mindist`: the minimum distance between Correlates of War states, in kilometers, in non-directed dyad-year format (1946-2015)
- `cow_nmc`: Correlates of War National Material Capabilities data (version 5.0)
- `cow_sdp_gdp`: (Surplus and Gross) Domestic Product for Correlates of War States
- `cow_states`: Correlates of War state system membership data (version: 2016)
- `cow_trade_sy`: Correlates of War state-year trade data (version 4.0)
- `gml_dirdisp`: directed dispute-year data from version 2.1.1 of the Gibler-Miller-Little inter-state dispute data.
- `gw_ddy`: a full directed dyad-year data frame of Gleditsch-Ward state system members
- `gw_mindist`: the minimum distance between  Gleditsch-Ward states, in kilometers, in non-directed dyad-year format (1946-2015)
- `gw_sdp_gdp`: (Surplus and Gross) Domestic Product for Correlates of War States
- `gw_states`: Gleditsch-Ward independent state system data (version: 2017)
- `maoz_powers`: Zeev Maoz' global/regional power data.
- `ucdp_onsets`: a state-year data set of UCDP armed conflict onsets/episodes.

@@

tic()
create_stateyears() %>%
  add_gwcode_to_cow() %>%
  add_ucdp_onsets() %>%
  add_capital_distance() %>%
  add_contiguity() %>%
  add_cow_majors() %>%
  add_cow_trade() %>%
  add_democracy() %>%
  add_igos() %>%
  add_minimum_distance(system = "cow") %>%
  add_archigos() %>%
  add_nmc() %>%
  add_sdp_gdp(system = "cow") 
toc()
